## Results {.tabset}
### Summary

#### Overlap of outliers

n
: neighbors (lof)

c
: contamination (lof)

s
: seed (downsampling)

r
: reads (downsampling)


```{r, fig-feature-feature-overlap}
readRDS("../plots/original/feature_summary.rds") %>%
  print()
```

#### Density for features (original)

```{r, fig-feature-lof-summary}
readRDS("../plots/feature_lof_summary.rds") %>%
  print()
```

M
: Mismatch score

D
: Deletion score

I
: Insertion score

{% for region in PRONTO["regions"] %}
{% if loop.first %}
### Region: {{region}} {.tabset}
{% else %}
### {{region}} {.tabset}
{% endif%}
{% for feature in config["jacusa2"]["features"] %}
{% if loop.first %}
#### Feature: {{feature}} {.tabset}
{% else %}
#### {{feature}} {.tabset}
{% endif%}
{% for lof in config["lof"] %}
{% if loop.first %}
##### *neighbors~{{lof["neighbors"]}}, contamination~{{lof["contamination"]}}*
{% else %}
##### *.~{{lof["neighbors"]}}, .~{{lof["contamination"]}}*
{% endif%}
<h4>Original</h4>
{% if config["downsampling"] %}
```{r, fig.align="center", fig-read-{{lof["neighbors"]}}-{{lof["contamination"]}}-{{feature}}-{{region}}-summary}
readRDS("../plots/downsampling_summary/neighbors~{{lof["neighbors"]}}_contamination~{{lof["contamination"]}}/feature~{{feature}}/{{region}}.rds") %>%
  print()
```
{% endif %}

```{r, fig.align="center", fig-feature-analysis-preprocessed-{{lof["neighbors"]}}-{{lof["contamination"]}}-{{feature}}-{{region}}-barplot}
readRDS("../plots/feature/original/preprocessed/neighbors~{{lof["neighbors"]}}_contamination~{{lof["contamination"]}}/feature~{{feature}}/{{region}}_barplot.rds") %>%
  print()
```

<!-- TODO: add is target -->

```{r, fig.align="center", fig-feature-analysis-preprocessed-{{lof["neighbors"]}}-{{lof["contamination"]}}-{{feature}}-{{region}}-table, results="asis"}
read.table("../plots/feature/original/preprocessed/neighbors~{{lof["neighbors"]}}_contamination~{{lof["contamination"]}}/feature~{{feature}}/{{region}}_outlier.tsv", header = TRUE, sep = "\t") %>%
  dplyr::select(seqnames, pos, ref, ref_context, mod, outlier_type) %>%
  dplyr::rename("seq. id" = "seqnames", "ref." = "ref", "ref. context" = "ref_context", "outlier type" = "outlier_type") %>%
  dplyr::mutate(mod = dplyr::recode(mod, "*" = "")) %>%
  knitr::kable() %>%
  kableExtra::kable_styling(full_width = FALSE)
```
{% if config["downsampling"] %}
<h4>Downsampling</h4>
{% for reads in config["downsampling"]["reads"] %}
<h5>Reads~{{reads}}</h5>
{% for seed in config["downsampling"]["seed"] %}
<h6>Seed~{{seed}}</h6>
```{r, fig.align="center", fig-feature-analysis-{{reads}}-{{seed}}-preprocessed-{{lof["neighbors"]}}-{{lof["contamination"]}}-{{feature}}-{{region}}-barplot}
readRDS("../plots/feature/downsampling/seed~{{seed}}_reads~{{reads}}/neighbors~{{lof["neighbors"]}}_contamination~{{lof["contamination"]}}/feature~{{feature}}/{{region}}_barplot.rds") %>%
  print()
```
```{r, fig.align="center", fig-feature-downsampling-{{reads}}-{{seed}}-{{lof["neighbors"]}}-{{lof["contamination"]}}-{{feature}}-{{region}}-table, results="asis"}
read.table("../plots/feature/downsampling/seed~{{seed}}_reads~{{reads}}/neighbors~{{lof["neighbors"]}}_contamination~{{lof["contamination"]}}/feature~{{feature}}/{{region}}_outlier.tsv", header = TRUE, sep = "\t") %>%
  dplyr::select(seqnames, pos, ref, ref_context, mod, outlier_type) %>%
  dplyr::rename("seq. id" = "seqnames", "ref." = "ref", "ref. context" = "ref_context", "outlier type" = "outlier_type") %>%
  dplyr::mutate(mod = dplyr::recode(mod, "*" = "")) %>%
  knitr::kable() %>%
  kableExtra::kable_styling(full_width = FALSE)
```
{% endfor %}
{% endfor %}
{% endif %}
{% endfor %}
{% endfor %}
{% endfor %}

