## Reads {.tabset}

### Counts {.tabset}

#### Regions: All

<h3>Preprocessed</h3>

```{r, fig-read-summary-total}
readRDS("../plots/read_summary/total_data.rds") %>%
  print()
```

<h3>Sequence IDs</h3>

```{r, fig-read-summary-total-seq-ids}
readRDS("../plots/read_summary/total_seq_ids.rds") %>%
  print()
```

{% if "downsampling" in config %}
<h3>Downsampling</h3>

```{r, fig-read-summary-downsampling}
readRDS("../plots/read_summary/total_downsampling.rds") %>%
  print()
```
{% endif %}

{% for region in PRONTO["regions"] %}
#### {{region}}

<h3>Preprocessed</h3>

```{r, fig-read-summary-{{region}}}
readRDS("../plots/read_summary/{{region}}_data.rds") %>%
  print()
```
{% if "downsampling" in config %}
<h3>Downsampling</h3>

```{r, fig-read-summary-{{region}}-downsampling}
readRDS("../plots/read_summary/{{region}}_downsampling.rds") %>%
  print()
```
{% endif %}

{% endfor %}

### Mapping

#### Mapped reads

```{r, fig-read-reads-mapped}
readRDS("../plots/samtools/stats/merged_SN_reads_mapped_summary.rds") %>%
  print()
```

#### Mapping quality

```{r, fig-read-mapq}
readRDS("../plots/samtools/stats/merged_MAPQ_summary.rds") %>%
  print()
```

#### Zero MAPQ reads

```{r, fig-read-reads-mq0}
p <- readRDS("../plots/samtools/stats/merged_SN_reads_MQ0_summary.rds")
pg <- ggplot2::ggplot_build(p)
if (!all(pg$data[[1]]$y == 0)) {
  print(p)
} else {
  cat("Not applicable")
}
```

### Properties

#### Read length

```{r, fig-read-length}
readRDS("../plots/samtools/stats/merged_RL_summary.rds") %>%
  print()
```

#### Average length

```{r, fig-read-average-length}
readRDS("../plots/samtools/stats/merged_SN_average_length_summary.rds") %>%
  print()
```

#### Average quality

```{r, fig-read-average-quality}
readRDS("../plots/samtools/stats/merged_SN_average_quality_summary.rds") %>%
  print()
```

#### Reads QC failed

```{r, fig-read-reads-qc-failed}
p <- readRDS("../plots/samtools/stats/merged_SN_reads_QC_failed_summary.rds")
pg <- ggplot2::ggplot_build(p)
if (!all(pg$data[[1]]$y == 0)) {
  print(p)
} else {
  cat("Not applicable")
}
```

### Substitutions

#### Error rate

```{r, fig-read-error-rate}
readRDS("../plots/samtools/stats/merged_SN_error_rate_summary.rds") %>%
  print()
```

#### Insertion length

```{r, fig-read-insertions}
readRDS("../plots/samtools/stats/merged_I_summary.rds") %>%
  print()
```

#### Deletion length

```{r, fig-read-deletions}
readRDS("../plots/samtools/stats/merged_D_summary.rds") %>%
  print()
```
